---
title: "ggplot_hook"
author: "zerocool"
date: "04/10/2023"
output: html_document
---

## Setting Up My Environment
Notes: setting up my environment by loading **tidyverse** and **palmerpenguins**
packages

```{r loading packages, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(palmerpenguins)
data("penguins")
```

```{r}
print(head(penguins))
```


## Creating ggplot for **flipper_length_mm** and **body_mass_g** column by species
Notes: Here  plotting creating scatterplot for relationship
between flipper_legth_mm and body_mass_g  by breakdown by species

```{r ggplot for penguin dataViz, message=FALSE, warning=FALSE, paged.print=FALSE}

ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(color="purple")
```


## Creating plot with point in shape based on species 
Note: here creating plot shape for each species different by
using shape aesthetics 

```{r ggplot shapebased on species, message=FALSE, warning=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))
```

## Flipper and body mass by species and sex
Here we plot flipper against body mass and look breakdown by species and sex 

```{r breakdown by species and sex, message=FALSE, warning=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```


## Flipper and body mass by species and sex dropping na values
Here we plot flipper against body mass and look breakdown
by species and sex and dropping na values

```{r message=FALSE, warning=FALSE}
penguins %>%
  drop_na(sex) %>%
  ggplot(data=penguins,mapping=aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(mapping=aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```



















